\textls[-0]{\thetitle}

### 2023-03-16 metatheory-condensed.tex
Reply comments. Fix.

\begin{itemize}
[labelsep=*,leftmargin=1pc,itemsep=3pt]
\item 
Linkages model families, so they are like tuples composed of fields
(with field names represented by variable bindings).
But there is a twist: linkages support late binding.
Unlike dependent tuples where a later component is \emph{existentially}
quantified over the earlier ones, a linkage component is \emph{universally}
quantified over---and thus polymorphic to---the components preceding it.\Zhixuan{explain the intuition behind the (typing rule of) linkages, and try to connect it to the ``family'' in the earlier section/surface syntax}\EDJreply{I am not sure if more is needed because the section ``Family polymorphism via linkages'' is trying to do this. Maybe I should estabilish connection between Rule l/add with the compilation process of fam poly?}\YZreply{I don't think you should mention anything about compilation process here. The surface syntax? Maybe. But I prefer not changing this sentence; it's supposed to be an executive summary rather than a detailed explanation.}

>>>>

\begin{itemize}
[labelsep=*,leftmargin=1pc,itemsep=3pt]
\item 
Linkages model families, so they are like tuples composed of fields
(with field names represented by variable bindings).
But there is a twist: linkages support late binding.
Unlike dependent tuples where a later component is \emph{existentially}
quantified over the earlier ones, a linkage component is \emph{universally}
quantified over---and thus polymorphic to---the components preceding it.\Zhixuan{explain the intuition behind the (typing rule of) linkages, and try to connect it to the ``family'' in the earlier section/surface syntax}\EDJreply{I am not sure if more is needed because the section ``Family polymorphism via linkages'' is trying to do this. Maybe I should estabilish connection between Rule l/add with the compilation process of fam poly?}\YZreply{I don't think you should mention anything about compilation process here. The surface syntax? Maybe. But I prefer not changing this sentence; it's supposed to be an executive summary rather than a detailed explanation.}\EDJreply{Actually I current am not sure where to add more sentences and how to elaborate more. Except for mentioning compilation process I don't think I have any good idea. So I will just stop here.}
